Reanalysis Step 5: Sensitivity Analysis with E-values

### 2025-08-26 reanalysis-3-propensity_scores.qmd
3 bug fix

  cat("#### Balance Summary Table\n\n")
  summary(twang_model) |> print() |> kable()
  cat("\n\n")
}
```

>>>>

  cat("#### Balance Summary Table\n\n")

  # Get balance statistics from the twang model
  # The bal.table function gives us the detailed balance statistics
  tryCatch({
    bal_table <- bal.table(twang_model, digits = 4)

    # Extract the summary statistics for the optimal stopping point
    # twang stores these in the desc slot
    es_mean_stats <- twang_model$desc$es.mean

    # Safely extract values with error checking
    safe_round <- function(x, digits = 4) {
      if (is.null(x) || !is.numeric(x)) return(NA)
      return(round(x, digits))
    }

    # Create a clean summary table
    summary_df <- data.frame(
      Metric = c("N Treated", "N Control", 
                 "ESS Treated", "ESS Control",
                 "Max ES", "Mean ES", "Max KS",
                 "Iterations"),
      Unweighted = c(
        es_mean_stats$n.treat,
        es_mean_stats$n.ctrl,
        es_mean_stats$n.treat,  # ESS = n for unweighted
        es_mean_stats$n.ctrl,    # ESS = n for unweighted
        safe_round(bal_table$unw$max.es, 4),
        safe_round(bal_table$unw$mean.es, 4),
        safe_round(bal_table$unw$max.ks, 4),
        NA
      ),
      Weighted = c(
        es_mean_stats$n.treat,
        es_mean_stats$n.ctrl,
        safe_round(es_mean_stats$ess.treat, 2),
        safe_round(es_mean_stats$ess.ctrl, 2),
        safe_round(bal_table$es.mean$max.es, 4),
        safe_round(bal_table$es.mean$mean.es, 4),
        safe_round(bal_table$es.mean$max.ks, 4),
        es_mean_stats$n.trees
      )
    )

    kable(summary_df, 
          caption = paste("Balance Summary for Imputation", i),
          align = c('l', 'r', 'r'))

  }, error = function(e) {
    # Fallback to simpler summary if bal.table fails
    cat("Note: Detailed balance table unavailable. Showing basic summary:\n\n")

    # Use the summary method which is more reliable
    sum_output <- summary(twang_model)

    # Try to extract key metrics from the summary
    if (!is.null(sum_output)) {
      print(sum_output)
    } else {
      cat("Balance statistics not available for this imputation.\n")
    }
  })

  cat("\n\n")
}
```

### 2025-08-26 reanalysis-5-sensitivity.qmd
3 bug fix

Key interpretations:
- **E-value**: The minimum strength of association on the risk ratio scale that an unmeasured confounder would need to have with both exposure and outcome to explain away the observed association
- **E-value for CI**: The minimum strength needed to shift the confidence interval to include the null

@@

**Main Effect of Lapsing on Vision Impairment:**  
- Odds Ratio: `r round(or_main, 3)`  
- 95% CI: (`r round(ci_lower_main, 3)`, `r round(ci_upper_main, 3)`)

@@

**Most robust finding:**  
- Subgroup: `r most_robust$DR_Severity` with `r most_robust$Treatment`  
- E-value: `r most_robust$E_Value_Point`

**Least robust finding:**  
- Subgroup: `r least_robust$DR_Severity` with `r least_robust$Treatment`  
- E-value: `r least_robust$E_Value_Point`

>>>>

Key interpretations:

- **E-value**: The minimum strength of association on the risk ratio scale that an unmeasured confounder would need to have with both exposure and outcome to explain away the observed association
- **E-value for CI**: The minimum strength needed to shift the confidence interval to include the null

@@

**Main Effect of Lapsing on Vision Impairment:**

- Odds Ratio: `r round(or_main, 3)`  
- 95% CI: (`r round(ci_lower_main, 3)`, `r round(ci_upper_main, 3)`)

@@

**Most robust finding:**

- Subgroup: `r most_robust$DR_Severity` with `r most_robust$Treatment`  
- E-value: `r most_robust$E_Value_Point`

**Least robust finding:**

- Subgroup: `r least_robust$DR_Severity` with `r least_robust$Treatment`  
- E-value: `r least_robust$E_Value_Point`
